Modeling site-specific amino-acid preferences deepens phylogenetic estimates of the divergence of viral proteins.

### 2018-04-06 manuscript/manuscript.tex
more work on the introduction

Phylogenetics is commonly used to estimate the time since the divergence of two lineages. 
Under the assumption of a molecular clock, branch lengths on the phylogenetic tree can be transformed into estimates of time. 
When a calibration points exists, these timing estimates of evolutionary events can be placed on an absolute timescale.

@@

Here we examined how ExpCM's and other forms of modeling purifying selection affects the estimates of deep divergence times of influenza virus hemagglutinin (HA). 
We found that models with site-specific measurements of purifying selection estimates longer deep branches. 
We find this extension of branch length is mostly independent from common method of account for purifying selection by rate variation. 
We also found that the ExpCM's estimated similar branch lengths to a site-specific model which infers the amino-acid preferences from the phylogenetic data~\citep{lartillot2004bayesian, rodrigue2014site}.
However, the results from these site-specific models are limited by an effect of purifying selection which is not accounted for in current models---how amino-acid preferences shift over time due to epistasis.

>>>>

Phylogenetics is commonly used to estimate the time since the divergence of two lineages. 
Under the assumption of a molecular clock~\citep{zuckerkandl1965}, the branch lengths on a phylogenetic tree can be transformed into estimates of time~\citep{yang2012molecular}. 
When a calibration point exists, these timing estimates of evolutionary events can be placed on an absolute timescale.

@@

Here we examined how ExpCM's and other forms of modeling purifying selection affects the estimates of deep divergence times of influenza virus hemagglutinin (HA). 
We found that models with site-specific measurements of purifying selection estimates longer deep branches. 
We found this extension of branch length is mostly independent from common method of account for purifying selection by rate variation. 
We also found that the ExpCM's estimated similar branch lengths to a site-specific model which infers the amino-acid preferences from the phylogenetic data~\citep{lartillot2004bayesian, rodrigue2014site}.
However, the results from these site-specific models are limited by an effect of purifying selection which is not accounted for in current models---how amino-acid preferences shift over time due to epistasis.
